Designing a virtual workplace\\
%What is a virtual workplace? What is important while designing one? Sträter zitieren!!
Before thinking about the technical feasability of the desired concept, the proactive design of the workplace for the human using the system has to be considered (Sträter and Bengler, 2019). \\
The virtual workplace contains a motion capturing suit and VR glasses. Both are liabilities for the user. A few aspects have to be regarded wearing the technical equipment. the glasses and suit should not be weared longer than (QUELLE). At the smallest feeling of dizziness the glasses should not be weared anymore (QUELLE). 
Immersion in virtual reality\\
%What is virtual reality?
The latin word "immersio" which means plunging into something is the original word for Immersion. A widely accepted defintion of Immersion according to McMahan (2003) is described by Jannet Murray (1997):\\
 Immersion is a metaphorical term derived from the physical experience of being submerged in water. We seek the same feeling from a psychologically immersive experience that we do from a plunge in the ocean or swimming pool: the sensation of being surrounded by a completely other reality, as different as water is from air, that takes over all of our attention, our whole perceptual apparatus . . . in a participatory medium, immersion implies learning to swim, to do the things that the new environment makes possible . . . the enjoyment of immersion as a participatory activity.
In the context of virtual reality a high level of immersion is aspired. In order to rate the level of immersion Brown and Cairns (2004) developed a theory which ranks the involvement of a player in a game in three stages:
Engagement
Engrossment
Total Immersion
Controlling Humanoid Robots\\
Controlling the robot with your own arm using a motion capturing suit and at the same time thinking the controlled arm is your own requires that the robotic arm contains all Degrees of Freedom (DoFs) the human arm has too. This rises the question how many DoFs a human arm has. According to (QUELLE) there are 6 DoFs as shown in (FIGURE). ALl six DoFs are simulated by a respective Servomotor. The existing robotic arm at the Institute A\& O has these six DOFs and the exact positions are shown in (FIGURE).
Robot kinematics
Motion Tracking
Human shape is one of the best shapes for robot remotely controlled.\cite{ieee_industrial_electronics_society_mfi_2003} 